---
title: "Homework 5"
author: Jeong lim Kim, Jayoung Kang, Hye-Min Jung
date: "5/20/2020"
fontsize: 10 pt
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      #include = TRUE, 
                      fig.width = 6, fig.height = 4,
                      results='markup',
                      warning = FALSE,
                      cache = TRUE,
                      digits = 3,
                      width = 48) 
```
We’ll explore casts for ‘drama’ movies from 1980-1999. I’ve limited the data to actors in more than ten productions over this time period (and to movies with more than ten actors).

[1] The actors network has an edge if the two actors were in the same movie. 
* Plot the entire actors network.
```{r, cache=TRUE}
## actors network example
library(igraph)

### GRAPH
## read in a graph in the `graphml' format: xml for graphs.
## it warns about pre-specified ids, but we want this here
## (these ids match up with the castlists in movies.txt)
actnet <- read.graph("actors.graphml",format="graphml")
actnet_edgelist <- as_edgelist(actnet, names = TRUE)
act_network <- graph.edgelist(actnet_edgelist, directed=FALSE)

faction_vertex_shape = get.vertex.attribute(act_network, "Faction")

act_network_degree = degree(act_network)

plot(act_network, 
     edge.arrow.size=.4, 
     vertex.shapes = faction_vertex_shape,
     vertex.size = act_network_degree / sum(act_network_degree)*200,
     vertex.label=NA, edge.curved=FALSE)
```

[2] Plot the neighborhoods for “Bacon, Kevin” at orders 1-3. 
* How does the size of the network change with order?
  + Adding one extra order creates a much bigger network.
```{r, cache=TRUE}
kb <- V(actnet)['Bacon, Kevin']
V(actnet)$color = "pink"
V(actnet)['Bacon, Kevin']$color <- "turquoise"
V(actnet)$frame.color = 0
V(actnet)$label.color = "black"
kblink1 <- graph.neighborhood(actnet, order = 1, nodes = kb)[[1]]
plot(kblink1, edge.curved=FALSE, vertex.label = NA)

kblink2 <- graph.neighborhood(actnet, order = 2, nodes = kb)[[1]]
plot(kblink2, edge.curved=FALSE, vertex.label = NA)

kblink3 <- graph.neighborhood(actnet, order = 3, nodes = kb)[[1]]
plot(kblink3, edge.curved=FALSE, vertex.label = NA)
```




```{r, cache=TRUE}
### TRANSACTION
## read in the table of actor ids for movies
## this is a bit complex, because the movie names
## contain all sorts of special characters.

movies <- read.table("movies.txt", sep="\t", 
	row.names=1, as.is=TRUE, comment.char="", quote="")

## it's a 1 column matrix.  treat it like a vector

movies <- drop(as.matrix(movies))

## each element is a comma-separated set of actor ids.  
## use `strsplit' to break these out

movies <- strsplit(movies,",")

## and finally, match ids to names from actnet

casts <- lapply(movies, 
	function(m) V(actnet)$name[match(m,V(actnet)$id)])

## check it

casts['12 Bucks']


## format as arules transaction baskets

library(arules)

casttrans <- as(casts, "transactions")

dim(casttrans) #14326 movies  6953 actors

## Set up STM information

castsize <- unlist(lapply(casts, function(m) length(m)))

## see ?rep.int: we're just repeating movie names for each cast member
?rep.int
acti <- factor(rep.int(names(casts),times=castsize))

## actors

actj <- factor(unlist(casts), levels=V(actnet)$name)

## format as STM (if you specify without `x', its binary 0/1)

actmat <- sparseMatrix(i=as.numeric(acti),j=as.numeric(actj),
		dimnames=list(movie=levels(acti),actor=levels(actj)))

## count the number of appearences by actor

nroles <- colSums(actmat)

names(nroles) <- colnames(actmat)

movierules <- apriori(casttrans,
                      parameter=list(support=0.0001, confidence=0.1, maxlen=2))

# maxlen defines the maximum number of items in each itemset of frequent items.

inspect(movierules)

inspect_movierules <- as.data.frame(inspect(movierules))

pairs <- labels(movierules)
head(pairs)
pairs <- gsub("\\{|\\}", "", pairs)
pairs <- strsplit(pairs, " => ")
pairs <- do.call(rbind,pairs)
pairs <- pairs[pairs[,1]!="",]
head(pairs) # this is edgelist! 

movienet <- graph.edgelist(pairs)
movienet <- as.undirected(movienet)
```

[3] 
* Who were the most common actors (have appeared the most in movies)? 
  +  Corrêa e Castro, Cláudio
```{r}
sort(degree(movienet), decreasing=T)
```
* Who were most connected? 
  + Dobtcheff, Vernon 
```{r, cache=TRUE}
sort(degree(actnet), decreasing=T)
```
* Pick a pair of actors and describe the shortest path between them.
  + Pair: from "Dennehy, Brian" to "Neill, Sam"
  + There's only 1 shortest path between Dennehy and Sam. (Dennehy, Brian Neill, Sam)
```{r, cache=TRUE}
all_shortest_paths(actnet, from="Dennehy, Brian", to="Neill, Sam")

DtoN <- get.shortest.paths(actnet, from="Dennehy, Brian", to="Neill, Sam")

DtoN[["vpath"]]

E(actnet)$width <- 2
E(actnet)$color <- "grey"
E(actnet, path=DtoN$vpath[[1]])$color <- "blue"
plot(actnet)
```


[4] Find pairwise actor-cast association rules with at least 0.01% support and 10% confidence. 
* Describe what you find.
  + There are densely connected groups, at least 5 community structure going on. 
```{r, cache=TRUE}
V(movienet)$color <- "cyan"

plot(movienet, vertex.label=NA, vertex.size=3, edge.curved=FALSE) 

#There are densely connected groups, at least 5 community structure going on. 
```









